An Automatic Verification Framework for Software Configurations

### 2016-05-08 OSDI/arch.tex
better arch

\para{Learning.}
The input of learner is a set of files that have been translated
into well-structured and typed representations.
The learner module employs a collection of learning algorithms
to generate various rule and constraints,
potentially used to handle different types of configuration errors.
These rules are the output of the learner, and will be 
used by the checker to detect errors.
By combining the translated representations and the learned
rules together, we already build a language model for
configuration verifications.
Because the translator outputs probabilistic typed entries,
the learner is responsible for determining a type for each entry.

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which needs users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class is looked as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.
\ennan{I do know we are using in some sense templates, but
we should use pattern or some words to persuade we are 
using an implicit ``templates''; otherwise, too similar 
to what EnCore did.}

Although the learner does necessarily rely on templates,
\app still offers a database to contain many templates,
as shown in Figure~\ref{fig-overview}.
Some of these templates are responsible for offering
specific system executional environment information.
It is widely known that any existing learning algorithm cannot
derive rules checking environment violation, \eg,
whether current account is the owner of a certain path.
In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment-related configuration errors.

\para{Checking.}
The checker is used to detect the rule violations in the configuration
files of interest. The inputs of checker are the learned rules 
and the target configuration file to verify.
Its outputs a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations, or a suspicious value.
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
\ennan{I really wanted to say we are using MaxSMT to check and rank
these errors ...}
In our experience, we find learned rules can be significantly reused
to check different configuration files, thus improving our usability.

>>>>

\para{Learning.}
The input of the learner is a set of files that have been translated
into well-structured and typed representations.
The learner module employs a collection of learning algorithms
to generate various rule and constraints,
potentially used to handle different types of configuration errors.
These rules are the output of the learner, and will be 
used by the checker to detect errors.
By combining the translated representations and the learned
rules together, we build a language model for
configuration verifications.
Because the translator outputs probabilistic typed entries,
the learner is responsible for determining a type for each entry.

Different from previous efforts, \eg, EnCore~\cite{zhang14encore},
which needs users or developers to provide explicit templates,
\app's learner encodes some predefined error-patterns 
to generate rules. 
As an illustration of a simple rule that we can learn,
consider an encoded pattern $X_1 \le X_2$, where $X_1$ and $X_2$ are
integer variables. The learner may derive the rule stating that
$\texttt{mysql.max\_persistent} \le \texttt{max\_connections}$. 
There is a classification and taxonomy of configuration errors in the 
existing work on automated configuration troubleshooting%
~\cite{yin11anempirical, configdataset}. 
Each class can be viewed as an error-pattern 
that \app should handle: we consider integer constraints, 
ordering errors, typing errors, correlation errors, etc.
\ennan{I do know we are using in some sense templates, but
we should use pattern or some words to persuade we are 
using an implicit ``templates''; otherwise, too similar 
to what EnCore did.}

Although the learner does necessarily rely on templates,
\app still offers a database containing many templates,
as shown in Figure~\ref{fig-overview}.
Some of these templates are responsible for offering
specific system executional environment information.
A learning algorithm cannot derive rules related to environment violations, \eg,
whether the current account is the owner of a certain path, without information 
about the environment. In order to deal with comprehensive misconfiguration problems,
the learner needs a template DB to provide environment information,
thus detecting system environment-related configuration errors.

\para{Checking.}
The checker is used to detect rule violations in the configuration
files of interest. The inputs of the checker are the learned rules 
and the target configuration file to verify.
It outputs a report (as shown in $\S$\ref{sec-motiv}) about 
whether it finds any error, \eg, rule violations, or a suspicious value.
As shown in Figure~\ref{fig-overview},
there are two sub-modules in the checker. They are responsible for
checking rule violations and suspicious values, respectively.
\ennan{I really wanted to say we are using MaxSMT to check and rank
these errors ...}
In our experience, we find learned rules can be significantly reused
to check different configuration files, thus improving our usability.
